Robots, Are They Overlords or Serf-Laborers?

### 2015-06-08 draft1.tex
Start Re-formating and Citing

\title{Sample Title} %Change Title

@@

\abstract{Of all the tools and methods invented by human kind to tame nature and make use of its challenges, the computer has had the greatest impact on society. Coupled with the Internet, computers have changed the way billions of humans work, entertain themselves, and think. Since the rise of the computers, Artificial Intelligence (AI) has been one of the most debated issues in the field of engineering. Research toward the creation of AI includes creation of self-aware machines that have superior intellectual abilities to that of human abilities. However, many researchers argue that the creation of AI will deeply change the society and will help human kind to solve major societal problems, while others refute the arguments for the conceptual invention because of ethical problems that AI will bring such as an anticipated human annihilation by these agents. This paper focuses on the the ethical problems that the creation of AI will raise.}

@@

\shorttitle{Short Title as per APA manual} %Change it

@@

@@

Anthropomorphism is the basis of AI which is the imitation of the way that humans find solutions for problems. As a result of this imitation process, anticipated outcomes are not only solving the problem itself, but also finding the optimal solution for the problem in shortest time period possible. This speed and ability to solve problems will be advantageous for human kind. In this section, the advantages of AI are discussed. 

@@

\subsection{The Last Invention of Human Kind That Researchers Forsee}

@@

From the very beginning of the conceptual designs of AI, it has been the most debated issue in the engineering and scientific societies due to its ethical problems. Near future is fecund to a dilemma which human kind will face in AI's moral integrity and its position in society (Duffy, 2006). This section synthesizes the ethical issues and counterarguments coping with them.

@@

\bibliography{file.bib}

>>>>

\title{Robots, Are They Overlords or Serf-Laborers?}

@@

% modify it!
\abstract{Of all the tools and methods invented by humankind to tame nature and make use of its challenges, the computer has had the greatest impact on society. Coupled with the Internet, computers have changed the way billions of humans work, entertain themselves, and think. Since the rise of the computers, Artificial Intelligence (AI) has been one of the most debated issues in the field of engineering. Research toward the creation of AI includes creation of self-aware machines that have superior intellectual abilities to that of human abilities. However, many researchers argue that the creation of AI will deeply change the society and it will help humankind to solve major societal problems, while others refute the arguments for the conceptual invention because of ethical problems that AI will bring such as an anticipated human annihilation by these agents. This paper focuses on the the ethical problems that the creation of AI will raise.} 

@@

\shorttitle{Overlords vs. Serf-Laborers}

@@

\section{New Synthesis}
Even though the term robot was coined two centuries ago and the idea of Artificial Intelligence (AI) emerged decades ago, some of the problems that have been raised by these two terms are yet to solved. Sometimes, solutions for any arbitrary problem can be solved by seeing the bigger picture rather than scrutinizing tiny details. Thus, this paper focuses on numerous definitions for these terms and various applications of AI.\par
By literary definition the term robot is derived from the Czech word "roboti" meaning serf-labor. However, this slave-like definition has altered to something brand new as technology advances. In this article entitled "The Sheer Difficulty of Defining What a Robot Is", \citeA{pear} discusses two distinctive definitions of Robotics that are posed by the prominent experts in the field of Robotics. These two definitions emphasize different aspect of Robotics creating important distinctions among them. The first definition puts emphasis on the successful combination of a rigid body responsible from interacting with its environment and a central reasoning unit responsible from reasoning tasks based perception and cognition. Without software and hardware collaboration, as \citeA{pear} cited in his article, accomplishing such tasks for a robot cannot be possible. The second definition, however, takes autonomy into account. A robot, \citeA{pear} quoted in his article, must have an detailed idea of any action formed by a tedious plan, accurate reasoning and precise action to interact with its physical environment. In light of these definitions, robots have to interact with its environment, which exclude any means of social interactions. However, \citeA{lan} asserts that socially interaction robots are significantly popular among society. Albeit popular, social robots, for instance a teacher robot or a guidance robot employed in an art gallery, seem to be decontextualized. This discrepancy brings about a major problem in individual and societal level. For instance, individuals have started to get strong advices from AI applications rather than a close friend who know better about the individual seeking advices, the taste of of music or book for instance, than a software crunching numbers faster than a man. Even though this issue seems to have a minor flipside, once it is aggregated, it will create true alienation from society and confussion regarding personhood, \citeA{lan} claims.\par

@@

Anthropomorphism is the basis of AI which is the imitation of the way that humans find solutions for problems. As a result of this imitation process, anticipated outcomes are not only solving the problem itself, but also finding the optimal solution for the problem in shortest time period possible. This speed and ability to solve problems will be advantageous for humankind. In this section, the advantages of AI are discussed. 

@@

\subsection{The Last Invention of humankind That Researchers Forsee}

@@

From the very beginning of the conceptual designs of AI, it has been the most debated issue in the engineering and scientific societies due to its ethical problems. Near future is fecund to a dilemma which humankind will face in AI's moral integrity and its position in society (Duffy, 2006). This section synthesizes the ethical issues and counterarguments coping with them.

@@

\bibliography{bibliography}
